Distribution of a Facebook application

### 2011-04-08 paper.tex
methodology

Figure \ref{fig:authorization} details how authorization and
authentication take place with OAuthDialog. The \textit{app server}
show cases the server on which the app is actually
running. \textit{Facebook} represents all the Facebook servers, on
which perform authentication and authorization. The \textit{OAuth
  Dialog} runs on the browser of the client who is going to use the
application.

@@

\subsection{Data from social graph (JSON-Objects)}
\label{sec:json-objects}

\section{Methodology}
\label{sec:method}

\subsection{The Quiz}
\label{sec:quiz}

\subsection{Data collection and evaluation}
\label{sec:data-coll-eval}

@@

\begin{center}
\begin{table}
\label{tab:coruser}
\begin{tabular}{l | c c c}
a & a & a & a \\

\hline
b & b & b & b
\end{tabular}
\caption{dummy}
\end{table}
\end{center}

>>>>

Figure \ref{fig:authorization} details how authorization and
authentication take place with OAuthDialog. The \textit{app server}
illustrates the server on which the app is actually
running. \textit{Facebook} represents all the Facebook servers, on
which perform authentication and authorization. The \textit{OAuth
  Dialog} runs on the browser of the client who is going to use the
application.

@@

\section{Methodology}
\label{sec:method}
In this section, the quiz is described as well as its
implementation. Then, it is explained how data are collected for
further analysis and how they can be evaluated.

\subsection{The Quiz}
\label{sec:quiz}
The quiz contains questions in German about dentistry health facts. Participants are asked 5
questions taken from a pool of 20 questions. Each question has 4
possible answers. Multiple selection is possible, but at least one
answer is correct. A question is answered correctly, if each correct
and no incorrect answer have been selected. Figure \ref{fig:quiz}
shows how the quiz looks like.

\begin{figure}
  \includegraphics[height=3in]{../img/fbquiz.png}
 \caption{The quiz.}
\label{fig:quiz}
\end{figure}

The quiz is competitive. After the quiz is completed, user are told
how good they were in comparison to other participants and to their
friends. As shown in figure \ref{fig:solution}, for each question the
correct solution is given. A user can also invite friends to
participate by clicking on the appropriate image. This is demonstrated in
figure \ref{fig:invite}.

\begin{figure}
  \includegraphics[width=3.5in]{../img/fbsolution.png}
  \caption{Solution of a question.}
\label{fig:solution}
\end{figure}

\begin{figure}
  \includegraphics[width=3.5in]{../img/fbinvite.png}
  \caption{This screenshot shows how friends can be invited.}
\label{fig:invite}
\end{figure}

\subsection{Implementation}
\label{sec:implementation}
The quiz-application detailed in the last section makes use of
Facebook's php-\ac{sdk} and JavaScript-\ac{sdk}. It requires
permissions for \textit{user$\_$birthday} and \textit{publish$\_$stream}.
Data used by the quiz are stored in a MySQL-database, tables have the
following contents:
\begin{itemize}
\item \textbf{User} - entries are created for each user who participates as
well as for each of a user's friends. A flag details if user
participated or not.
\item \textbf{Friendships} - creates entries for each friendship found in
users' friend lists.
\item \textbf{Questions} - contains the questions of the quiz.
\item \textbf{Answers} - contains the possible answers and a flag to mark them
as correct or false.
\item \textbf{Given answers} - stores each answer given by a user.
\item \textbf{User score} - stores the score user had in the quiz.
\item \textbf{Correct answered questions} - stores which questions were correct
answered by which user.
\end{itemize}

The database queries are performed with the PHP
pear\footnote{http://pear.php.net/}-package. The script which performs
the queries uses few files: The index.php manages the application
flow. The library.php contains all the functions needed, and quiz.php,
question.php, and quizResult.php display the quiz as well as the
correct solution and the feature to invite friends.

\subsection{Data collection}
\label{sec:data-coll-eval}

\subsection{Data evaluation}
\label{sec:data-evaluation}

@@

% \begin{center}
% \begin{table}
% \label{tab:coruser}
% \begin{tabular}{l | c c c}
% a & a & a & a \\

% \hline
% b & b & b & b
% \end{tabular}
% \caption{dummy}
% \end{table}
% \end{center}
